% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt, letterpaper]{article}
\usepackage[letterpaper,margin=0.4in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

Austin A. Valentine 
  austin.a.valentine@gmail.com
405.664.4011
	 /austin-valentine 
 
SKILLS									
	 
❖	Git
❖	TFVC 
❖	Subversion (SVN)
❖	Frontend
❖	Backend
❖	Full-Stack
❖	YAML | TOML
❖	SQL | T-SQL | PL/SQL 
❖	Oracle Database
❖	MS SQL-Server
❖	HTML5
❖	CSS3 | Sass | Less
❖	Bootstrap
❖	JavaScript | jQuery
❖	Node.js
❖	TypeScript
❖	React
❖	Vite.js
❖	Postman
❖	Bruno
❖	Swagger
❖	Flutter
 
❖	PHP
❖	ASP.Net (C#, VB)
❖	Sahi UI Testing
❖	ReST | SOAP | OData APIs
❖	Model-View-Controller (MVC)
❖	Responsive Web De-sign
❖	Infrastructure as Code (IaC)
❖	GitLab | GitHub | Az-ure DevOps
❖	Confluence
❖	DevOps & DORA Met-rics
❖	Agile
❖	SCRUM Master (CSM)
❖	KanBan
❖	Design Patterns
❖	Backend for Frontend (BFF)
❖	Cloud Computing
❖	Bash
❖	PowerShell
❖	Java
❖	Go
❖	Dart
❖	Google Apps Script
❖	ERP (SAP)
 
❖	Object-Oriented Pro-gramming (OOP)
❖	Functional Program-ming
❖	Object-Relational Mapping (Entity Framework)
❖	Object-Object Mapping Tools (AutoMapper)
❖	Dependency Injection | Inversion of Control
❖	Continuous Integra-tion/Continuous De-livery (CI/CD)
❖	Test Driven Develop-ment (TDD)
❖	Automated Browser Testing Software (Sa-hi)
❖	Unobtrusive client-side dynamics
❖	Digital Decisioning Platforms (Decisions)
❖	Robotics Process Au-tomation (RPA) (Ui-Path)
❖	Service Oriented Ar-chitectures | Micro-services
❖	Modular Monolith Architecture
❖	Event-Driven Archi-tectures
❖	Event Notifica-tion
❖	Event Sourcing
❖	Event-carried State Transfer
❖	Command-Query Responsibility Segregation (CQRS)
❖	Work and Project Management Plat-forms (Jira|Asana)
 
WORK EXPERIENCE									
Midland Mortgage of MidFirst Bank - Oklahoma City, OK	2021 – Present 
Senior Programmer Analyst

•	Led effort to extract 75K+ lines of redundant code to make reusable, shared components with much greater flexi-bility and less than half lines of code, reducing dev cycle time and testing cycle time while increasing automated test coverage and quality.
•	Solutioned Personally-Identifiable Information (PII) generation and emulation methods for mortgage customer website to engage outside consultants without compromising sensitive customer information.
•	Develop customer-facing web applications serving 500K FHA, RHS, VA, and Conventional mortgagors.
•	Integrate external websites with internal mortgage information systems to improve overall customer service while reducing the cost of servicing.
•	Coach team to adopt more Agile practices and tools using Azure DevOps and JIRA.
•	Design configurable mortgagor alert module drastically reducing time to deliver new loan alerts without project manager or developer time.
•	Build Azure DevOps Classic and YAML pipeline infrastructure to automate code package and app deliveries.
•	Enhance knowledge worker collaboration and project efficiency through effective documentation of domain and tribal knowledge.

Midland Mortgage of MidFirst Bank - Oklahoma City, OK 	2019 –2021
Senior Business Analyst

•	Managed, built, and implemented workflow automation projects using Decisions including group access control, central dashboard and reporting, UI forms, and external integrations with internally hosted & external vendor sys-tems.
•	Learned Decisions low-code digital decisioning platform and UiPath Robotics Process Automation for work-flow/business process automations.

ECS Federal, LLC, United States Postal Service - Norman, OK 	2014 – 2019
Database / Web Application Developer / Scrum Master

•	Learned Sahi helping transition team by pioneering automated browser end-to-end & UI testing for a complex en-terprise application catching 10s of defects before Production release within the first few cycles.
•	Initiated automated Unit Testing and Continuous Integration/Continuous Delivery using Jenkins. 
•	Led and supported team of 6 as first acting SCRUM Master developing new features on multiple high profile enter-prise applications. 
•	Led transition to Agile SCRUM practices, balancing competing business interests, technical debt, lack of experience in Agile process thinking, and individual skills growth to progress value and velocity.

Harris IT Services, United States Postal Service - Norman, OK 	2013 – 2013 
(CONTINUED ABOVE WITH ECS)
Database / Web Application Developer

•	Learned PHP, Oracle PL/SQL, & JavaScript frameworks/plugins (JQuery/Highcharts/etc.)
•	3-tiered web development architecture decoupling display, business processing, and data access layers (MVC)
•	Worked in highly modular application environment in which all modules were fully self-contained for use in oth-er web sites/applications.
•	PL/SQL ETL scripts for Data Warehousing / Reporting through distributed database architecture.

Devon Energy Corporation - Oklahoma City, OK 		2011 – 2012
Windows 7 Program / IT Asset Management
DBA / Developer / Analyst 

•	Designed Ad Hoc Solutions for project managers to coordinate Users, Computers, Applications (with delivery methods) during the Beta and Pilot periods.
•	Assisted in designing the production solution for full-scale deployment of Windows 7 and related technologies.
•	Gained experience with application, desktop, and user virtualization using specific technologies such as Citrix Xe-nApp, Citrix XenDesktop, Microsoft AppV, and AppSense.
•	Changed endpoint computing architecture from device-centric to device agnostic, cloud-based.

EDUCATION									
 
University of Oklahoma

	Bachelor of Business Administration 
	Management Information Systems | Accounting 

 
 

 
  

AUSTIN VALENTINE
Oklahoma City, OK
405.664.4011
austin.a.valentine@gmai.com	REFERENCES
Mark Delgado
Senior Software Engineer
Love’s Travel Stops
Oklahoma City, OK
405.996.7315 | sandmdelgados@gmail.com
Associate
Colleague worked together at US Postal Service under ECS Federal, LLC

Myles Koertje
Decisions Workflow Supervisor
MidFirst Bank
Oklahoma City, OK
405.757.7121 | myles.koertje@midfirst.com
Associate
Colleague Decisions workflow analysis and development at MidFirst Bank

Greg Waters
ByeBuyBooks, LLC  …
Norman, OK
405.410.9005 | greg@jackpratt.com
Friend, fellow parishioner and IS/automation customer

Eric Bradshaw
Database Administrator
MidFirst Bank
Oklahoma City, OK
405.618.3995 | eric.bradshaw@midfirst.com
Associate
Worked closely with Database related admin, deployment and continuous appli-cation design improvements 

	

More references can be provided upon request


